\thispagestyle{acknowledgements}
\section*{Acknowledgments}
\label{sec:acknowledgments}
\addcontentsline{toc}{section}{Acknowledgements}

It is with immense gratitude that I acknowledge the support and help from my supervisors from both the IBM CIC Groningen, Arjen van Veen and Arne Rutjes, as well as prof. dr. Dimka Karastoyanova and dr. Vasilios Andrikopoulos, from the Rijksuniversiteit Groningen for their valuable suggestions, ever encouraging and motivating guidance, as well as the trust deposited in me during the span of this project is something I will forever cherish.

A special word goes to dr. Vasilios, for helping me overcome all the limitations faced during this project, and for being available as much as one can be, to provide me with detailed feedback on this manuscript as well as during the course of this Master project.

I consider it an honor to have performed this work under the opportunity provided to me by IBM, a company that has given me all the tools necessary to conduct my research.

I wish to thank the University of Groningen, for allowing me to develop myself in order to become a better student, thinker and person.

I would still like to extend my gratitude to all of the IBM professionals I had the chance to contact with, as well as the people that have taken the time of evaluating my system during its development.

I wish to dedicate this thesis first and foremost to my girlfriend, Rita Gaspar, for pushing me everyday to give my all in any circumstance. To my family, for supporting me every single day and allowing me to fulfil my dreams. To my friends José Vicente, Inês Paredes and Diogo Nogueira, for their support, constant friendship and care. To all of you, I would like to say a few words in my mother tongue, Portuguese: "\textit{Eu amo-vos muito e espero ter-vos deixado orgulhosos}".

Gostaria de dedicar esta tese em primeiro lugar à minha namorada, Rita Gaspar, por me motivar todos os dias e a dar tudo de mim em todas as circunstâncias. À minha familia, por me apoiarem todos os dias e permitirem-me atingir os meus sonhos. Aos meus amigos José Vicente. Maria Inês Paredes e Diogo Nogueira, pelo constante apoio, amizade e carinho. A todos vocês gostaria de dizer que vos amo muito e espero ter-vos deixado orgulhosos.